### 2021-04-07 Supplementary_Material/Table_1_List_of_Studies.Rmd
last edits

---
title: ""
output:
  pdf_document: default
  html_document: default
---
\begin{landscape}

@@

Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", "Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", "Ecuador", "New Zealand", "Venezuela",
"USA", "Ecuador")

@@

references <- data.frame(`First author`, `Number of networks`, `Network type`, `Network structure`, Year, Country, DOI)

colnames(references) <- c("First author", "Network N°", "Type", "Structure", "Year", "Country", "DOI")

kable(references, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 9, full_width=F)
```

\end{landscape}

>>>>

---
title: ""
output:
  pdf_document: default
  html_document: default
---

@@

#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
#"USA", "Ecuador")

@@

references <- data.frame(`First author`, `Number of networks`, `Network type`, `Network structure`, Year,  DOI)

colnames(references) <- c("First author", "N°", "Type", "Structure", "Year",  "DOI")

kable(references, "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 8, full_width=F)
```
